### 2021-12-02 manuscript.tex
Update metadata [ci skip]
This build is based on
https://github.com/lubianat/quali_phd/commit/b00405796db47b9b3cdee9651d1d5273e977fd3e.

This commit was created by the following CI build and job:
https://github.com/lubianat/quali_phd/commit/b00405796db47b9b3cdee9651d1d5273e977fd3e/checks
https://github.com/lubianat/quali_phd/actions/runs/1530538872

This manuscript
(\href{https://lubianat.github.io/quali_phd/v/6be5c637bc2c3d7dcaab4728fbb4091baf10abbf/}{permalink})
was automatically generated
from \href{https://github.com/lubianat/quali_phd/tree/6be5c637bc2c3d7dcaab4728fbb4091baf10abbf}{lubianat/quali\_phd@6be5c63}
on December 2, 2021.

@@

\begin{itemize}
\item
  \textbf{John Doe}
  \includegraphics{images/orcid.svg}
  \href{https://orcid.org/XXXX-XXXX-XXXX-XXXX}{XXXX-XXXX-XXXX-XXXX}
  · \includegraphics{images/github.svg}
  \href{https://github.com/johndoe}{johndoe}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/johndoe}{johndoe}
  Department of Something, University of Whatever
  · Funded by Grant XXXXXXXX
\item
  \textbf{Jane Roe}
  \includegraphics{images/orcid.svg}
  \href{https://orcid.org/XXXX-XXXX-XXXX-XXXX}{XXXX-XXXX-XXXX-XXXX}
  · \includegraphics{images/github.svg}
  \href{https://github.com/janeroe}{janeroe}
  Department of Something, University of Whatever; Department of Whatever, University of Something
\end{itemize}

>>>>

This manuscript
(\href{https://lubianat.github.io/quali_phd/v/b00405796db47b9b3cdee9651d1d5273e977fd3e/}{permalink})
was automatically generated
from \href{https://github.com/lubianat/quali_phd/tree/b00405796db47b9b3cdee9651d1d5273e977fd3e}{lubianat/quali\_phd@b004057}
on December 2, 2021.

@@

\begin{itemize}
\tightlist
\item
  \textbf{Tiago Lubiana}
  \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-2473-2313}{0000-0003-2473-2313}
  · \includegraphics{images/github.svg}
  \href{https://github.com/lubianat}{lubianat}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/lubianat}{lubianat}
  School of Pharmaceutical Sciences, University of São Paulo; Ronin Institute
  · Funded by Grant \#2019/26284-1 from the São Paulo Research Foundation (FAPESP).
\end{itemize}
